Turbulence in compact to giant H~II regions

### 2023-04-27 strucfunc_paper.tex
Finish second subsection on NGC 595 and 604

In Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
The model-derived parameters are \(\sigma\pos^2 = \SI{53 \pm 5}{km^{2}.s^{-2}}\),
\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.4 \pm 0.2\).
The value of the observed \(\sigma\pos^2 = \SI{44}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\) and \(r_0 = \SI{11}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{21}{pc} \).
The maximum \(B(r)\) value is \SI{104}{km^{2}.s^{-2}} at a separation of \SI{30}{pc}. 
%For NGC 595 we see that the structure function plateau at this maximum \(B(r)\) value, which implies that the observed \(\sigma\pos^2\) is affected by the observational constraints.
Until \(r_0 \sim \SI{55}{pc} \) the structure functions remains closely to the 'true' \(2\sigma\pos^2\), for the largest scale there is a decrease between  \(\SI{55}{pc} < r < \SI{110}{pc} \) where the structure function plateaus at the 'observed' \(2\sigma\pos^2\). 
Above \SI{110}{pc} we see a very disperse downturn  until \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
The seeing (RMS) is \SI{2.1}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and there are no points below this value.
Considering the first point to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{1.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.27} and \num{1.18}, respectively, while our derived value is \num{1.38}.

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
The value of the observed \(\sigma\pos^2 = \SI{55}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{86}{km^{2}.s^{-2}}\) and \(r_0 = \SI{12}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{30}{pc} \).
The maximum \(B(r)\) value is \SI{143}{km^{2}.s^{-2}} at a separation of \SI{55}{pc}. 
NGC 604 structure function presents clear pattern of periodic oscillations between  \(\SI{30}{pc} < r < \SI{211}{pc} \).
The spatial wavelength is \SI{ \sim 50}{pc}. 
The minimum value of this periodic pattern is \SI{54}{km^{2}.s^{-2}} at \SI{135}{pc} 
and finally it goes back up again at \SI{211}{pc} to a \(B(r)\) value of \SI{123}{km^{2}.s^{-2}}.
The seeing is \SI{2.1}{pc} (\(s_0\)=\SI{1.2}{\arcsecond}) and the first three points structure function are below these value, which means that the seeing is heavily affecting this observations.
This also is shown by the big difference bee tween the 'true model' (green dahed line) and our 'model' (solid orange lines).
onsidering the first point above this \(s_0\) value to be valid, which corresponds to \SI{10}{km^{2}.s^{-2}} at \(r = \SI{3}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.40} and \num{1.03}, respectively, while our derived value is \num{1.2}.

>>>>

In Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
The model-derived parameters are \(\sigma\pos^2 = \SI{53 \pm 5}{km^{2}.s^{-2}}\),
\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.4 \pm 0.2\).
The velocity variance is slightly higher than the observed value of \SI{44}{km^{2}.s^{-2}},
indicative of a moderate finite box effect.
At the largest scales, the structure function trends slowly downwards,
which may be due to a radial decline in the amplitude of the turbulent velocity field,
but the effect is less marked than in other regions, such as Orion.

In  Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
The model-derived parameters are \(\sigma\pos^2 = \SI{84 \pm 20}{km^{2}.s^{-2}}\),
\(r_0 = \SI{12 \pm 6}{pc} \)), and \(m = 0.8 \pm 0.2\).
Again the model-derived velocity variance is higher than the observed value of \SI{55}{km^{2}.s^{-2}},
which this time is due primarily to the fact that the
derived correlation length is only 6 times higher than the RMS seeing width,
so some of the small-scale fluctuation power is missing from the observations.
Of all our sources, NGC~604 shows the largest difference between the inferred
``true'' structure function and the observed one, so the derived parameters
should be treated with caution.
At the largest scales, the structure function shows a pronounced minimum
at \(r \approx {150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx {300}{pc}\),
which is slightly larger than the size of the map.
